---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# skimrExtra

<!-- badges: start -->
<!-- badges: end -->

The goal of skimrExtra is to provide examples of extension to the skimr package.

## Installation

You can install the released version of skimrExtra from github. 

``` r
devtools::install_github("elinw/skimrExtra")
```

## Using skimrExtra

The `skimr` package provides a compact summary of data in a data frame or 
object that can be coerced to a data frame.  The summary provides an
an opinionated list of statistics for many of the most commonly used data
types (based on the `class()` of a variable).  This package, skimrExtra, extends
this to some additional types both as examples of how to do this and in response
to some common requests for additional data types.

For example, objects using produced by the `sf` (simple features) package 
include (one or more) columns representing geometries.  These are in
geographic formats and not standard. In `skimr` these fall back to the default
type of character, while `skimrExtra` supports them directly,
assuming that the `sf` package is installed.  

```{r example}
library(skimr)
if (requireNamespace("sf", quietly = TRUE)){
  library(sf)
  nc <- st_read(system.file("shape/nc.shp", package = "sf"))
  skim(nc)
}
```

Support for variables of the class `haven_labelled` is also included. This 
support simply identifies the underlying data type using `typeof()` and 
assumes the user will manage further processing if desired.

```{r}
library(skimrExtra)
## basic example code
if (requireNamespace("sf", quietly = TRUE)){
  skim(nc)
}


```

Generally speaking, the skimr API should be extended in packages that wish
to use it rather than relying on the `skimr` or `skimrExtra` maintainers. 
Doing so allows much greater customization. Instructions for this are 
included in the `skimr` "Supporting additional objects" vignette.


## Utility functions

The package also includes a utility function `skim_to_var_table()` which
produces a more compact data frame than does the standard `skim()` 
function by casting statistics with shared names to strings and placing
them in a single column. 

```{r}
skim_to_var_table(CO2) %>% knitr::kable()
```

compared to

```{r}
skim(CO2)
```


## Plans

It may be that this package will add support for other data types, sets of
skimmers, statistics and utilities.  Pull requests in these categories are 
welcome and will be considered on a case by case basis. Contributions should
include full documentation and tests. 

Please note that the 'skimrExtra' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
